Under-approximation of reachability in multivalued asynchronous networks

### 2013-04-02 parts/def-ph.tex
note on inconclusiveness and TODO on complexity

We note that cooperative sorts are standard PH sorts and do not involve any
special treatment regarding the semantics of related actions.
Furthermore, it is possible to chain cooperative sorts in order to express more complex cooperations
or to decrease the number of processes created within each cooperative sort,
as this number is exponential in the number of sorts that cooperate.
%to prevent the combinatoric explosion of the number of processes created within cooperative sorts.
%Such constructions are helpful as the static analysis of dynamics developed does not suffer from the number of sorts,
%but on the number of processes within a single sort.

>>>>

We note that cooperative sorts are standard PH sorts and do not involve any
special treatment regarding the semantics of related actions.
Furthermore, it is possible to chain cooperative sorts in order to express more complex cooperations or
to decrease the number of processes created within each cooperative sort,
as the static analysis method developed in \pref{sec:sa} does not suffer from the number of sorts but from the number of processes in one sort.
%as this number is exponential in the number of sorts that cooperate.
%to prevent the combinatoric explosion of the number of processes created within cooperative sorts.
%Such constructions are helpful as the static analysis of dynamics developed does not suffer from the number of sorts,
%but on the number of processes within a single sort.

### 2013-04-02 parts/sa.tex
note on inconclusiveness and TODO on complexity

@@

@@

  This unwanted behaviour is palliated by the semantics of PH with priorities proposed in this paper.
  Indeed, the under-approximation given in \pref{th:approxinf} does not conclude regarding the reachability of $c_1$,
  as one of the edges of the resulting graph of local causality is not coherent (\pref{def:coherent}),
  as shown in in \pref{fig:sa-livelock}.

>>>>

\todo{Complexité de la construction du GLC}

@@

\todo{Complexité de la vérification du GLC}

@@

  This unwanted behaviour is palliated by the semantics of PH with priorities proposed in this paper.
  Indeed, the under-approximation given in \pref{th:approxinf} does not conclude regarding the reachability of $c_1$,
  as one of the edges of the resulting graph of local causality is not coherent (\pref{def:coherent}),
  as shown in in \pref{fig:sa-livelock}.
  (However, from the inconclusiveness of \pref{th:approxinf}, one cannot conclude about the unreachability of $c_1$.
  Such analysis should be driven for instance with over-approximation methods developed in~\cite{PMR10-TCSB}.)
